---
title: "Webinar 2 Homework"
author: "Shane Cone @Microscone"
date: "12/19/2019"
output: html_document
---
Here are the answers to the homework. For the most part, the code is quite similar to the compiled code from the last chunk of the webinar. However, there are a couple of changes. The full code is in this first chunk, and the chunk below delves into something new!

```{r fig.dim = c(15, 10)}
library(tidyverse)
library(ggplot2)
library(lubridate)

Monitoring_data <- read_csv("Homework_Hourly Monitoring Data for R_Simplified.csv", na = c("NoData", "<Samp", "Down", "NA"), skip = 3)
Monitoring_Ozone <- Monitoring_data %>% 
  select(c(1:7, 11, 13)) 
Monitoring_Ozone$Date <- mdy(Monitoring_Ozone$Date)
Monitoring_Ozone <-  Monitoring_Ozone %>% 
  mutate(Timestamp = as_datetime(paste(Monitoring_Ozone$Date, Monitoring_Ozone$Time))) %>% 
  select(-Date, -Time)
Monitoring_long <-  gather(Monitoring_Ozone,"Station", "Ozone_ppm", 1:7)
Monitoring_long$Station <- as.factor(Monitoring_long$Station)
Monitoring_long$Station <- recode_factor(Monitoring_long$Station, `Bellefonte II Ozone ppm` = "Bellefonte II", `Brandywine Creek State Park Ozone ppm` = "Brandywine Creek State Park", `Killens Pond Ozone ppm` = "Killens Pond", `Lewes Ozone ppm` = "Lewes", `Lums Pond State Park Ozone ppm` = "Lums Pond State Park", `Martin Luther King Ozone ppm` = "Martin Luther King", `Seaford Ozone ppm` = "Seaford Ozone ppm")
ggplot(Monitoring_long, aes(x = Timestamp, y = Ozone_ppm, color = Station)) +
  geom_line() +
  theme_classic()

```

# Further Discussion

Here is the major new piece that was added. I repeated the whole code chunk so that the chunk below can be run as a whole.

```{r}

#repeated code start:
Monitoring_data <- read_csv("Homework_Hourly Monitoring Data for R_Simplified.csv", na = c("NoData", "<Samp", "Down", "NA"), skip = 3)
Monitoring_Ozone <- Monitoring_data %>% 
  select(c(1:7, 11, 13)) 
Monitoring_Ozone$Date <- mdy(Monitoring_Ozone$Date)
Monitoring_Ozone <-  Monitoring_Ozone %>% 
  mutate(Timestamp = as_datetime(paste(Monitoring_Ozone$Date, Monitoring_Ozone$Time))) %>% 
  select(-Date, -Time)
#repeated code end


#I gave the variables useful, recognizable names. Always a good practice!
Monitoring_long <-  gather(Monitoring_Ozone,"Station", "Ozone_ppm", 1:7) 

#then, I change the character names of the station into factors. This is a new data type for you! As we've said, R is a statistical program, and know how to "think" about categorical variables. Read the documentation for the as.factor function! 
Monitoring_long$Station <- as.factor(Monitoring_long$Station)

#Next, I want to change the names of the factors. I added "ppm" to the ozone variable name, so the station names don't need it! Also, one of our variables is "ozone", so there is no need to have "ozone" in each place name! Also, since it is now a factor, I don't have to so some sort of find and replace, I can just "recode" the factor, and it will change all of the names! 
Monitoring_long$Station <- recode_factor(Monitoring_long$Station, `Bellefonte II Ozone ppm` = "Bellefonte II", `Brandywine Creek State Park Ozone ppm` = "Brandywine Creek State Park", `Killens Pond Ozone ppm` = "Killens Pond", `Lewes Ozone ppm` = "Lewes", `Lums Pond State Park Ozone ppm` = "Lums Pond State Park", `Martin Luther King Ozone ppm` = "Martin Luther King", `Seaford Ozone ppm` = "Seaford Ozone ppm")

#you can check your factor levels this way:
levels(Monitoring_long$Station)
```
